### 2018-10-01 ms.tex
Add an internal glossary.

@@

In both cases we examined performance metrics for both the withheld prevalence data and the withheld incidence data.
As there is no good way of combining predictive error from both types of data into one performance metric, we considered performance separately throughout.
We considered the ability to predict incidence correctly out main objective.
However, a problem with using polygon data in a cross-validation scheme is that a model can perform well at the polygon level but not correctly predict the pixel-level malaria risk.
Predictive performance on prevalence points is one way to measure how well a model can predict pixel-level malaria risk.
However, in areas of low prevalence, small or moderately sized prevalence surveys can be noisy or unsensitive and so care must be taken when interpreting predictive performance on these data.
Our main performance metric was mean absolute error (MAE) for incidence and MAE weighted by survey sample size for prevalence.
While other metrics could have been used, we specifically did not use correlation as correlation measures linear dependance without regard to slope or intercept.
As the models are being fitted on data on difference scales we found that predictions were sometimes correlated but strongly displaced from the one-one line and therefore correlation metrics were misleading.
% Why not correlation
To assess how well the models were calibrated we considered coverage of the 80\% predictive credible intervals on the hold-out data.

@@

We have compared the predictive performance of a disaggration model and a model that jointly learns from aggregated incidence data and point prevalence surveys.
With regards to a random cross-validation scheme, adding points to the disaggregation model improved performance in one of three countries (Madagascar).
With regards to a spatial cross-validation scheme, which tests a models ability to predict malaria risk far away from available data, we found that adding the point surveys improved the disaggregation models in both PseudoSenegal and Madagascar but not Indonesia.

A problem with using cross-validation on polygon data is that a model could correctly predict polygon-level incidence while incorrectly predicting the within-polygon, pixel-level risk which is the real target of inference.
Of the four cases where polygon predictions were improved or remained similar after adding point data (Indonesia and Madagascar random cross-validation and PseudoSenegal and Madagascar spatial cross validation) the predictive performance on prevalence points was always unchanged or marginally improved.
However, the benchmark points-only model was the top or equal top model at predicting point level prevalence in four out of six cases and only marginally worse in one further case.
Only in the Madagascar, spatial cross-validation experiment was the points-only model notably worse at predicting prevalence.

>>>>

% Glossary
% Models:
%   Joint model
%   Polygon-only model
%   Point-only model
% Data:
%   Prevalence point-surveys
%   Polygon incidence
% Variables:
%   Pixel-level prevalence
%   Polygon-level incidence
%   Pixel-level incidence

@@

In both cases we examined performance metrics for both the withheld prevalence data and the withheld incidence data.
As there is no good way of combining predictive error from both types of data into one performance metric, we considered performance separately throughout.
We considered the ability to predict aggregated incidence correctly our main objective and our performance metric was mean absolute error (MAE)..
However, a problem with using polygon data in a cross-validation scheme is that a model can perform well at the polygon level but not correctly predict the pixel-level malaria risk.
Predictive performance on prevalence points is one way to measure how well a model can predict pixel-level malaria risk.
However, in areas of low prevalence, small or moderately sized prevalence surveys can be noisy or unsensitive and so care must be taken when interpreting predictive performance on these data.
Therefore our secondary metric was, MAE weighted by survey sample size, of prevalence point surveys.
While other metrics could have been used, we specifically did not use correlation as correlation measures linear dependance without regard to slope or intercept.
As the models are being fitted on data on difference scales we found that predictions were sometimes correlated but strongly displaced from the one-one line and therefore correlation metrics were misleading.
% Why not correlation
To assess how well the models were calibrated we considered coverage of the 80\% predictive credible intervals on the hold-out data.

@@

We have compared the predictive performance of a disaggration model and a model that jointly learns from aggregated incidence data and point prevalence surveys.
We found that neither model was clearly superior to the other but that both models recovered the broad spatial pattern of malaria risk (Figures \ref{predobsmapidn} and \ref{predobsmapidn}).
With regards to a random cross-validation scheme, adding points to the disaggregation model only improved performance in  Madagascar (Table~\ref{table1}).
With regards to a spatial cross-validation scheme, which tests a models ability to predict malaria risk far away from available data, we found that adding the point surveys improved the disaggregation models in both PseudoSenegal and Madagascar but not Indonesia  (Table~\ref{table2}).

We used held-out prevalence point-surveys to measure how well model were predicting the within-polygon, pixel-level malaria risk.

Of the four cases where polygon predictions were improved or remained similar after adding point data (Indonesia and Madagascar random cross-validation and PseudoSenegal and Madagascar spatial cross validation) the predictive performance on prevalence point-surveys was always unchanged or marginally improved.
However, the benchmark points-only model was the top or equal top model at predicting point-level prevalence in four out of six cases and only marginally worse in one further case.
Only in the Madagascar, spatial cross-validation experiment was the points-only model notably worse at predicting prevalence.
